### 2022-06-22 paper.Rmd
minor stuff

Table 1 displays the global simulation results aggregated across all conditions. Standard k-means performed best at minimizing discrepancy with regard to means ($\Delta \mathit{M}$), but disregarded all other distribution characteristics, where it did not outperform a random assignment. K-plus anticlustering also addressed $\Delta \mathit{M}$ quite well and at the same time minimized discrepancy with regard to the standard deviations ($\Delta \mathit{SD}$); all three k-plus approaches outperformed all other methods with regard to minimizing $\Delta \mathit{SD}$.

As Figure 1 shows, with increasing $N$, k-means and all k-plus methods converge on minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus term in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering is capable of addressing multiple objectives simultaneously, it is apparent that increasing the number of optimization criteria aggravated fulfilling each single criterion. K-plus skew/kurtosis and k-plus correlation performed worse at minimizing discrepancy with regard to standard deviations than standard k-plus, which itself performed slightly worse than k-means anticlustering. Still, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

>>>>

Table 1 displays the global simulation results aggregated across all conditions. Standard k-means performed best at minimizing discrepancy with regard to means ($\Delta \mathit{M}$), but did not outperform a random assignment with regard to all other distribution characteristics; replicating @papenberg2020, k-means' performance with regard to similarity in standard deviations was even below that of a random assignment. K-plus anticlustering addressed $\Delta \mathit{M}$ almost as well as k-means, and at the same time minimized discrepancy with regard to the standard deviations ($\Delta \mathit{SD}$); all three k-plus approaches outperformed all other methods with regard to minimizing $\Delta \mathit{SD}$.

As Figure 1 shows, with increasing $N$, k-means and all k-plus methods converge on minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus term in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering is capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria apparently aggravates fulfilling each single criterion. K-plus skew/kurtosis and k-plus correlation performed worse at minimizing discrepancy with regard to standard deviations than standard k-plus, which itself performed slightly worse than k-means anticlustering. Still, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.
